% =============================
% Academic CV Template (LaTeX)
% With horizontal rules below section titles
% =============================

\documentclass[11pt,a4paper]{article}

% --- Packages ---
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{parskip}

% --- Section formatting ---
\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.2ex plus .2ex}{0.8ex}

% --- Custom commands ---
\newcommand{\cvsection}[1]{\section*{#1}}
\newcommand{\cvsubsection}[1]{\subsection*{#1}}
\newcommand{\years}[1]{\textit{#1}} % For year ranges

% =============================
\begin{document}

% --- Header ---
\begin{center}
  {\LARGE Your Full Name} \\[4pt]
  \href{mailto:you@university.edu}{you@university.edu} $\vert$ (+1) 555-123-4567 \\
  Department of XYZ, Prestigious University \\
  \href{https://your-website.example}{your-website.example} $\vert$ ORCID: 0000-0000-0000-0000
\end{center}

\vspace{1em}

% --- Education ---
\cvsection{Education}
\textbf{Ph.D., Field of Study}, University Name, City, Country \hfill \years{2018--2024} \\
Dissertation: ``Title of Dissertation'' (Advisor: Prof. X)

\textbf{M.Sc., Field of Study}, University Name, City, Country \hfill \years{2016--2018}

\textbf{B.Sc., Field of Study}, University Name, City, Country \hfill \years{2012--2016}

% --- Research Interests ---
\cvsection{Research Interests}
High-dimensional inference; diffusion models; stochastic differential equations; Bayesian methods; applications to astronomy and physics.

% --- Research Experience ---
\cvsection{Research Experience}
\textbf{Graduate Research Assistant}, University Name, Lab/Group \hfill \years{2018--2024} \\
Advisor: Prof. X \\
\begin{itemize}[leftmargin=*]
  \item Developed methods for XYZ, resulting in N first-author publications.
  \item Collaborated with international teams on project ABC.
\end{itemize}

% --- Teaching Experience ---
\cvsection{Teaching Experience}
\textbf{Teaching Assistant}, Course Name, University Name \hfill \years{2020--2021}
\begin{itemize}[leftmargin=*]
  \item Led weekly tutorials for ~30 undergraduate students.
  \item Designed assignments and graded coursework.
\end{itemize}

% --- Publications ---
\cvsection{Publications}
(Use your citation style; chronological order, reverse-chronological order is common.)
\begin{enumerate}[leftmargin=*]
  \item Your Name, Coauthor. ``Title of Paper.'' \emph{Journal Name}, vol. X, pp. Y--Z, Year.
  \item Your Name. ``Another Title.'' \emph{Conference Proceedings}, Year.
\end{enumerate}

% --- Awards & Fellowships ---
\cvsection{Awards and Fellowships}
\begin{itemize}[leftmargin=*]
  \item Fellowship Name, Granting Organization \hfill \years{2023--2024}
  \item Best Paper Award, Conference Name \hfill \years{2022}
\end{itemize}

% --- Service & Outreach ---
\cvsection{Service and Outreach}
\begin{itemize}[leftmargin=*]
  \item Reviewer for journals: Journal A, Journal B.
  \item Organizer, Graduate Student Seminar Series, University Name.
  \item Outreach volunteer, STEM programs for high school students.
\end{itemize}

% --- References ---
\cvsection{References}
Available upon request. (Or list 2--3 referees with title, affiliation, and contact info.)

\end{document}

