\begin{enumerate}[leftmargin=*]
    \itemsep-0.5em
    \item C. Stone, \underline{\textbf{A. Adam}}, A. Coogan, L. Perreault-Levasseur, Y. Hezaveh.
        ``caskade: building Pythonic scientific simulators.''
        \emph{Journal of Open Source Software}, vol.~10, pp.~8786, (2025).  
    \item \underline{\textbf{A. Adam}}, C. Stone, C. Bottrel, R. Legin, Y. Hezaveh, L. Perreault-Levasseur. 
        ``Echoes in the Noise:  Posterior Samples of Faint Galaxy Surface Brightness Profiles with Score-Based Likelihoods and Priors.''
        \emph{The Astrophysical Journal (ApJ)}, vol.~169 (5), pp.~254, (2025).
    \item C. L. Rhea, J. Hlavacek-Larrondo, \underline{\textbf{A. Adam}}, R. Kraft, Á. Bogdán, L. Perreault-Levasseur, M. Prunier
        ``Deconvolving X-Ray Galaxy Cluster Spectra Using a Recurrent Inference Machine.''
        \emph{The Astrophysical Journal (ApJ)}, vol.~169 (5), pp.~268, (2025).
    \item G. M. Barco, \underline{\textbf{A. Adam}}, C. Stone, Y. Hezaveh, L. Perreault-Levasseur.
        ``Tackling the Problem of Distributional Shifts: Correcting Misspecified, High-Dimensional Data-Driven Priors for Inverse Problems.''
        \emph{The Astrophysical Journal (ApJ)}, vol.~980 (1), pp.~108, (2024).
    \item C. Stone, \underline{\textbf{A. Adam}}, A. Coogan, M.J. Yantovski-Barth, A. Filipp, L. Setiawan, C. Core, R. Legin, C. Wilson, G. M. Barco, Y. Hezaveh, L. Perreault-Levasseur. 
        ``Caustics: A Python Package for Accelerated Strong Gravitational Lensing Simulations.''
        \emph{The Journal of Open Source Software}, vol.~9 (103), pp.~7081, (2024).
    \item S. Venkatraman, M. Jain, L. Scimeca, M. Kim, M. Sendera, M. Hasan, L. Rowe, S. Mittal, P. Lemos, E. Bengio, \underline{\textbf{A. Adam}}, J. Rector-Brooks, Y. Bengio, G. Berseth, N. Malkin.
        ``Amortizing intractable inference in diffusion models for vision, language, and control.''
        \emph{Proceedings of the Conference on Neural Information Processing Systems (NeurIPS)}, 
        vol.~37, pp.~76080-76114, (2024).
    \item M. Sendera, M. Kim, S. Mittal, P. Lemos, L. Scimeca, J. Rector-Brooks, \underline{\textbf{A. Adam}}, Y. Bengio, N. Malkin.
        ``Improved off-policy training of diffusion samplers.''
        \emph{Proceedings of the Conference on Neural Information Processing Systems (NeurIPS)}, 
        vol.~37, pp.~81016-81045, (2024).
    \item R. Legin, \underline{\textbf{A. Adam}}, Y. Hezaveh, L. Perreault-Levasseur. 
        ``Beyond Gaussian Noise: A Generalized Approach to Likelihood Analysis with non-Gaussian Noise.''
        \emph{The Astrophysical Journal Letters (ApJL)}, vol.~949 (2), L41, (2023).
    \item \underline{\textbf{A. Adam}}, Y. Hezaveh, L. Perreault-Levasseur, M. Welling.
        ``Pixelated Reconstruction of Foreground Density and Background Surface Brightness in Gravitational Lensing Systems using Recurrent Inference Machines.''
        \emph{The Astrophysical Journal (ApJ)}, vol.~951 (1), pp.~6, (2023).
\end{enumerate}
