\begin{enumerate}[leftmargin=*]
    \itemsep-0.5em
    \item S. Venkatraman, M. Jain, L. Scimeca, M. Kim, M. Sendera, M. Hasan, L. Rowe, S. Mittal, P. Lemos, E. Bengio, \underline{\textbf{A. Adam}}, J. Rector-Brooks, Y. Hezaveh, L. Perreault-Levasseur, Y. Bengio, G. Berseth, N. Malkin.
        ``Amortizing intractable inference in diffusion models for Bayesian inverse problems.''
        \emph{NeurIPS Workshop on Machine Learning and the Physical Sciences}, (2025).
    \item A. Bourdin, R. Legin, M. Ho, \underline{\textbf{A. Adam}}, Y. Hezaveh, L. Perreault-Levasseur.
        ``Inpainting Galaxy Counts onto N-Body Simulations over Multiple Cosmologies and Astrophysics.''
        \emph{ICML Workshop on AI for Science}, (2024).
    \item \underline{\textbf{A. Adam}}, C. Stone, C. Bottrell, R. Legin, Y. Hezaveh, L. Perreault-Levasseur.
        ``Echoes in the Noise: Posterior Samples of Faint Galaxy Surface Brightness Profiles with Score-Based Likelihoods and Priors.''
        \emph{NeurIPS Workshop On Machine Learning and the Physical Sciences Workshop}, (2023). 
    \item N. Dia, M.J. Yantovski-Barth, \underline{\textbf{A. Adam}}, M. Bowles, P. Lemos, A. MM Scaife, Y. Hezaveh, L. Perreault-Levasseur.
        ``Bayesian Imaging for Radio Interferometry with Score-Based Priors.''
        \emph{NeurIPS Workshop on Machine Learning and the Physical Sciences}, (2023).
    \item R. Legin, M. Isi, K. Wong, \underline{\textbf{A. Adam}}, L. Perreault-Levasseur, Y. Hezaveh.
        ``Towards Unbiased Gravitational-Wave Parameter Estimation using Score-Based Likelihood Characterization.''
        \emph{2nd ICML Workshop on Machine Learning for Astrophysics}, (2023).
    \item \underline{\textbf{A. Adam}}, A, Coogan, N. Malkin, R. Legin, L. Perreault-Levasseur, Y. Hezaveh, Y. Bengio.
        ``Posterior samples of source galaxies in strong gravitational lenses with score-based priors.''
        \emph{NeurIPS Workshop on Machine Learning and the Physical Sciences}, (2022).
    \item \underline{\textbf{A. Adam}}, L. P.-Levasseur, Y. Hezaveh.
        ``Pixelated Reconstruction of Gravitational Lenses using Recurrent Inference Machines.''
        \emph{ICML Workshop on Machine Learning for Astrophysics}, (2022).
\end{enumerate}
